Reformulating phylogenetic mixed models to improve flexibility and speed

### 2018-10-16 main.tex
add ord 2010 ref on random slopes

\bmb{I think you need a lot more here; what does a random slopes model mean? You have one sentence that says ``people should be thinking about random slopes''. Then you talk about correlation (which is a much more subtle/less important issue, I think).}
In classic GLMM (without phylogenetic relationships), random slopes models are not always appropriate, but they are relevant over a wider range of scenarios than people are currently thinking about \cite{schielzeth2008conclusions, cleasby2015quantifying}.
When analyzing relationships among species between traits and environmental variables, it is entirely plausible that change in effect of predictor variables have on traits are changing in a phylogenetically correlated way.
In fact, it is easier to interpret random slopes in the evolutionary process context (i.e, are size of different species phylogenetically correlated, or growth rate through time of different species phylogenetically correlated?)
\mli{I like to think of it in a longitudinal setting of observing plant length/height. At time zero, they are all still seeds, one can imagine the growth rate are different plant species grow in a phylogenetically correlated way (similar species have similar growth rates).}
It may be easier to simplify the phylogenetic relationships (at the random slopes level) and think about the random-slopes model in a strictly hierarchical setting (i.e., estimating different slopes for each family, or taxon \cite{bunnefeld2012island}) - the PGLMM collapses to a standard random-slopes model. 
Users should be aware of two important questions when fitting random-slope models: How much data do we need in order to practically estimate the random slopes? and Are we making a mistake by ignoring random slopes \cite{schielzeth2008conclusions}? 
However, in the PGLMM context, as long as there's variation in the predictor among tips, there will be variation among taxa at some level, so random-slopes models will (almost always) be \emph{theoretically} identifiable.

>>>>

\bmb{I think you need a lot more here; what does a random slopes model mean? You have one sentence that says ``people should be thinking about random slopes''. Then you talk about correlation (which is a much more subtle/less important issue, I think).}
In classic GLMM (without phylogenetic relationships), random slopes models are not always appropriate, but they are relevant over a wider range of scenarios than people are currently thinking about \cite{schielzeth2008conclusions, cleasby2015quantifying,ord2010adaptation}.
When analyzing relationships among species between traits and environmental variables, it is entirely plausible that change in effect of predictor variables have on traits are changing in a phylogenetically correlated way.
In fact, it is easier to interpret random slopes in the evolutionary process context (i.e, are size of different species phylogenetically correlated, or growth rate through time of different species phylogenetically correlated?)
\mli{I like to think of it in a longitudinal setting of observing plant length/height. At time zero, they are all still seeds, one can imagine the growth rate are different plant species grow in a phylogenetically correlated way (similar species have similar growth rates).}
It may be easier to simplify the phylogenetic relationships (at the random slopes level) and think about the random-slopes model in a strictly hierarchical setting (i.e., estimating different slopes for each family, or taxon \cite{bunnefeld2012island}) - the PGLMM collapses to a standard random-slopes model. 
Users should be aware of two important questions when fitting random-slope models: How much data do we need in order to practically estimate the random slopes? and Are we making a mistake by ignoring random slopes \cite{schielzeth2008conclusions}? 
However, in the PGLMM context, as long as there's variation in the predictor among tips, there will be variation among taxa at some level, so random-slopes models will (almost always) be \emph{theoretically} identifiable.
